---
title: "Independent Research"
author: "Jacob Feinas"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r, warning = FALSE}
library(tidyverse)
library(readxl)
```

## Original Data
```{r, echo = FALSE}
originalData <- read_excel("2022 COC Panel Fixed.xlsx")
```


## Academic Planning
```{r, message=FALSE, warning=FALSE}
APC <- data.frame(full = c(
"BOSER,BETH L - CASSH CST Asc Tnr - Conv",
"DREGNE,WHITNEY KLARYN - CSH Mth Asc Tnr",
"GENDREAU,THOMAS B - CSH CS Asc Tnr",
"KOSIAK,JENNIFER J - CSHe Mth Prf Tnr",
"NANDIALATH,ANUP MENON - CBA Mgt Asc Tnr",
"PARMETER,GREGORY GEORGE - CASSH ThA Ast",
"ROLFHUS,KRISTOFER R - CSH Chm Prf Tnr",
"STEINER,LINDSAY B - CASSH Eng Asc Tnr",
"TROST,JENNIFER A - CASSH His Asc Tnr",
"KEEFE,ANNA VENDLA - CASSH GCL Asc Tnr - Alt",
"KOMISSAROV,SERGEY A - CBA Acc Asc Tnr - Alt",
"PANDE,VIVEK V - CBA Acc Asc Tnr - Alt"))

APC <- APC %>% separate(full, c("name", "deptrank", "note"), " - ")
APC <- APC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

APC.res.ind <- which(originalData$LastName %in% APC$name)

originalData$APC[APC.res.ind] <- "RES"

APC.res.ind
```

## Academic Technology
```{r, message=FALSE, warning=FALSE}
ATC <- data.frame(full = c(
"BELLAR,WENDI RENEE - CASSH CST Ast",
"BEYER,KEITH D - CSH Chm Prf Tnr",
"CHEN,SONG - CSH Mth Asc Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"ERAMUDUGODA GAMAGE,RANDIKA SANJEEWA - CBA Mgt Ast",
"GREINER,THOMAS - CSH Hpf Asc Tnr",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"KIM,EDWARD D - CSH Mth Asc Tnr",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"KOPP,BRYAN M - CASSH Eng Asc Tnr",
"KRAGE,VALERIE ANNE - SOE Eds AscTe",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"LEVINSON,LINDA C - CASSH Art Prf Tnr",
"LU,WEIXU - CASSH CST Ast",
"MITRA,DIPANKAR - CSH CS Ast",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"RAES,NICHOLAS ADAM - CASSH CST Lec",
"SCHWARTZ,CHRISTINE P - CSH Bio Asc Tnr",
"STOBB,WILLIAM E - CASSH Eng Prf Tnr",
"SVOBODA,VICTORIA A - CASSH SAA Asc Tnr Chr",
"THAKKAR,TANVI D - CASSH Psy Lec",
"TUROV,YEVGENIYA - CSH Chm AscTe",
"VAUGHN,CODY NATHANIEL - CBA Ecn Ast",
"WHITNEY,EMILY A - CSH HEd Asc Tnr",
"ZHANG,LEI - CASSH Eng Asc Tnr"))

ATC <- ATC %>% separate(full, c("name", "deptrank", "note"), " - ")
ATC <- ATC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

ATC.res.ind <- which(originalData$LastName %in% ATC$name)

originalData$ATC[ATC.res.ind] <- "RES"
```

## Academic Policies and Standards
```{r, message=FALSE, warning=FALSE}
CAPS <- data.frame(full = c(
"ANNINO,DAVID - CBA IS AscTe",
"CURRENT,MICHAEL D - CASSH Lib Ast Tnr",
"HARDY,PENELOPE KATE - CASSH His Ast",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"LIU,SHIANG - CBA Fin Ast",
"NEUKOM,JOSHUA D - CSH Chm AscTe",
"VEERASAMY,SUTHAKARAN - CASSH Psy Ast Tnr"))

CAPS <- CAPS %>% separate(full, c("name", "deptrank", "note"), " - ")
CAPS <- CAPS %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

CAPS.res.ind <- which(originalData$LastName %in% CAPS$name)

originalData$CAPS[CAPS.res.ind] <- "RES"
```

## CGAAF
```{r, message=FALSE, warning=FALSE}
CGAAF <- data.frame(full = c(
"BIGEL,ALAN I - CASSH Pol Prf Tnr",
"BUTLER MODAFF,JENNIFER - CASSH CST Asc Tnr",
"CRUTCHFIELD,SUSAN - CASSH Eng Asc Tnr",
"DEASON,GRACE M - CASSH Psy Asc Tnr",
"DICKMEYER,LINDA B - CASSH CST Prf Tnr Chr",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"KIM,EDWARD D - CSH Mth Asc Tnr",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"KOPP,BRYAN M - CASSH Eng Asc Tnr",
"KORTENKAMP,KATHERINE V - CASSH Psy Asc Tnr",
"LEAHY,RONDA L - CASSH CST Prf Tnr",
"LONGHURST,JAMES L - CASSH His Prf Tnr",
"MATCHETT,ANDREW J - CSH Mth Asc Tnr",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NARCOTTA-WELP,EILEEN M - CSH ESS Asc Tnr",
"STAPLETON,ANDREW H - CBA Mgt Prf Tnr",
"VEERASAMY,SUTHAKARAN - CASSH Psy Ast Tnr",
"ZHANG,LEI - CASSH Eng Asc Tnr"))

CGAAF <- CGAAF %>% separate(full, c("name", "deptrank", "note"), " - ")
CGAAF <- CGAAF %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

CGAAF.res.ind <- which(originalData$LastName %in% CGAAF$name)

originalData$CGAAF[CGAAF.res.ind] <- "RES"
```

## Ethics Advisory
```{r, message=FALSE, warning=FALSE}
EAC <- data.frame(full = c(
"ASCENCIO,CHRISTINE ALICE - CBA Mgt Ast",
"BELLAR,WENDI RENEE - CASSH CST Ast",
"BIGEL,ALAN I - CASSH Pol Prf Tnr",
"BUTLER MODAFF,JENNIFER - CASSH CST Asc Tnr",
"CEDERGREN,ANDERS R - CSH HEd Ast Tnr",
"CLUPPERT,INGA JOHANNA - CSH Hpf AstCl",
"DAMALI,UZAY - CBA Mgt Ast",
"GARCIA,MERIDETH MARIE - CASSHe Eng Ast",
"GREINER,THOMAS - CSH Hpf Asc Tnr",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"JOHNSON,KARI L - CSH Mic AstCl",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"KOPP,BRYAN M - CASSH Eng Asc Tnr",
"LAUFENBERG,MAGGIE R - CSH Hpf AstCl",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NASIF,NESE - CBA Mkt Ast",
"PARMETER,GREGORY GEORGE - CASSH ThA Ast",
"PETERSON,JESSICA MARIE - CASSH CST AstTe",
"ROBERTS,CHARLOTTE E - SOEe Eds Ast",
"SCHNEIDER,DANIEL C - CASSH Phl Ast",
"THAKKAR,TANVI D - CASSH Psy Lec",
"VEERASAMY,SUTHAKARAN - CASSH Psy Ast Tnr",
"WAGNER,SHELDON ERIC - CSH ESS AscTe"))

EAC <- EAC %>% separate(full, c("name", "deptrank", "note"), " - ")
EAC <- EAC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

EAC.res.ind <- which(originalData$LastName %in% EAC$name)

originalData$EAC[EAC.res.ind] <- "RES"
```

## Faculty Development
```{r, message=FALSE, warning=FALSE}
FDC <- data.frame(full = c(
"HARDY,PENELOPE KATE - CASSH His Ast",
"LEACH,MEGAN - CBA Acc Ast",
"NANDIALATH,ANUP MENON - CBA Mgt Asc Tnr",
"PARMETER,GREGORY GEORGE - CASSH ThA Ast",
"PAUDEL,SHISHIR KUMAR - CBA Fin Ast",
"TUROV,YEVGENIYA - CSH Chm AscTe",
"WHITNEY,EMILY A - CSH HEd Asc Tnr",
"XU,HONGYING - CASSH GCL Asc Tnr"))

FDC <- FDC %>% separate(full, c("name", "deptrank", "note"), " - ")
FDC <- FDC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

FDC.res.ind <- which(originalData$LastName %in% FDC$name)

originalData$FDC[FDC.res.ind] <- "RES"
```

## Graduate Academic Program Review
```{r, message=FALSE, warning=FALSE}
GAPR <- data.frame(full = c(
"DAMALI,UZAY - CBA Mgt Ast",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"MITRA,DIPANKAR - CSH CS Ast"))

GAPR <- GAPR %>% separate(full, c("name", "deptrank", "note"), " - ")
GAPR <- GAPR %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

GAPR.res.ind <- which(originalData$LastName %in% GAPR$name)

originalData$GAPR[GAPR.res.ind] <- "RES"
```

## General Education
```{r, message=FALSE, warning=FALSE}
GEC <- data.frame(full = c(
"BOSER,BETH L - CASSH CST Asc Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"DUTTA,NABAMITA - CBA Ecn Prf Tnr",
"GENDREAU,THOMAS B - CSH CS Asc Tnr",
"HARDY,PENELOPE KATE - CASSH His Ast",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"KOPP,BRYAN M - CASSH Eng Asc Tnr",
"LEACH,MEGAN - CBA Acc Ast",
"MIKA,TERESA LOUISE WHITWORTH - CSH Bio AstTe",
"MITRA,DIPANKAR - CSH CS Ast",
"PARMETER,GREGORY GEORGE - CASSH ThA Ast",
"PEKDEMIR,RECEP - CBA Acc Ast",
"SCHNEIDER,DANIEL C - CASSH Phl Ast",
"TORIBIO,SHERWIN G - CSH Mth Asc Tnr",
"VEERASAMY,SUTHAKARAN - CASSH Psy Ast Tnr"))

GEC <- GEC %>% separate(full, c("name", "deptrank", "note"), " - ")
GEC <- GEC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

GEC.res.ind <- which(originalData$LastName %in% GEC$name)

originalData$GEC[GEC.res.ind] <- "RES"
```

## General Education Assessment
```{r, message=FALSE, warning=FALSE}
GEAC <- data.frame(full = c(
"CEDERGREN,ANDERS R - CSH HEd Ast Tnr",
"CLUPPERT,INGA JOHANNA - CSH Hpf AstCl",
"DAMALI,UZAY - CBA Mgt Ast",
"FLEMING,ANNA MARIE - SOE FExp Lec",
"HARDY,PENELOPE KATE - CASSH His Ast",
"KOPP,BRYAN M - CASSH Eng Asc Tnr",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"LEACH,MEGAN - CBA Acc Ast",
"MITRA,DIPANKAR - CSH CS Ast",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NEUKOM,JOSHUA D - CSH Chm AscTe",
"PETERSON,JESSICA MARIE - CASSH CST AstTe",
"RAES,NICHOLAS ADAM - CASSH CST Lec"))

GEAC <- GEAC %>% separate(full, c("name", "deptrank", "note"), " - ")
GEAC <- GEAC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

GEAC.res.ind <- which(originalData$LastName %in% GEAC$name)

originalData$GEAC[GEAC.res.ind] <- "RES"
```

## Graduate Council
```{r, message=FALSE, warning=FALSE}
Gradcouncil <- data.frame(full = c(
"BRUNDAGE,CORD MICHAEL - CSH Bio Lec",
"CLUPPERT,INGA JOHANNA - CSH Hpf AstCl"))

Gradcouncil <- Gradcouncil %>% separate(full, c("name", "deptrank", "note"), " - ")
Gradcouncil <- Gradcouncil %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

Gradcouncil.res.ind <- which(originalData$LastName %in% Gradcouncil$name)

originalData$Gradcouncil[Gradcouncil.res.ind] <- "RES"
```

## IAS
```{r, message=FALSE, warning=FALSE}
IAS <- data.frame(full = c(
"BHATTACHARYYA,BASUDEB - CSH Chm AscTe",
"CHEN,SONG - CSH Mth Asc Tnr",
"CLUPPERT,INGA JOHANNA - CSH Hpf AstCl",
"DAMALI,UZAY - CBA Mgt Ast",
"ESKEW,STEWART SCOTT - CASSH Phl Lec",
"HART,KAREN STUART - CASSH Eng PrfTe",
"LAZZARI,MICHAEL A - CSH Mic AscCl",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NEUKOM,JOSHUA D - CSH Chm AscTe",
"OLSON,MICHELLE R - CSH Hpf AstCl",
"PETERSON,JESSICA MARIE - CASSH CST AstTe",
"RAES,NICHOLAS ADAM - CASSH CST Lec",
"REDMAN,RENEE S - CSH Bio PrfTe",
"SCHAAF,LUKE J - CASSH Eng AscTe",
"TUROV,YEVGENIYA - CSH Chm AscTe"))

IAS <- IAS %>% separate(full, c("name", "deptrank", "note"), " - ")
IAS <- IAS %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

IAS.res.ind <- which(originalData$LastName %in% IAS$name)

originalData$IAS[IAS.res.ind] <- "RES"
```

## IAS Promotion Committee
```{r, message=FALSE, warning=FALSE}
IASPC <- data.frame(full = c(
"BORAH,NILAKSHI - CBA Fin Asc Tnr",
"GOLDEN,BENJAMIN JAMES - CASSH ThA AscTe",
"MORRISON,HEIDI - CASSH His Asc Tnr"))

IASPC <- IASPC %>% separate(full, c("name", "deptrank", "note"), " - ")
IASPC <- IASPC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

IASPC.res.ind <- which(originalData$LastName %in% IASPC$name)

originalData$IASPC[IASPC.res.ind] <- "RES"
```

## International Education
```{r, message=FALSE, warning=FALSE}
IEC <- data.frame(full = c(
"BABAKHANI TEIMOURI,SHEIDA - CBA Ecn Asc Tnr",
"BELLAR,WENDI RENEE - CASSH CST Ast",
"BORJA RABAGO,JONATHAN - CASSH Mus Asc Tnr",
"BOSER,BETH L - CASSH CST Asc Tnr",
"CEDERGREN,ANDERS R - CSH HEd Ast Tnr",
"CROSBY,ELIZABETH M - CBA Mkt Asc Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"DOBBS,WARD C - CSH ESS Ast",
"ESKEW,STEWART SCOTT - CASSH Phl Lec",
"GHEIDI,NAGHMEH - CSH ESS Ast Tnr",
"GIBLIN,NAOKO AMINAKA - CSH ESS Asc Tnr",
"GOODNOW,REGINA R - CASSH Pol Asc Tnr Chr",
"GREANY,KRISTIN A - CSH Bio AscTe",
"HAN,YE - CBA IS Ast",
"HEASER,SARA A - CASSH Eng AscTe",
"HER,VINCENT K - CASSH Ant Asc Tnr",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"KABASHI,LEMA - SOEe Eds Asc Tnr",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"LAN,HAIXIA W - CASSH Eng Prf Tnr",
"LAUFENBERG,MAGGIE R - CSH Hpf AstCl",
"LEVINSON,LINDA C - CASSH Art Prf Tnr",
"LU,WEIXU - CASSH CST Ast",
"MISHRA,NITI BHUSHAN - CSH Geo Asc Tnr",
"MITRA,DIPANKAR - CSH CS Ast",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NANDIALATH,ANUP MENON - CBA Mgt Asc Tnr",
"PEACOCK,ELIZABETH A - CASSH Ant Asc Tnr",
"PEKDEMIR,RECEP - CBA Acc Ast",
"PFITZINGER,SCOTT G - CASSH Lib Ast Tnr",
"SAMBU,DANIEL K - CSH Geo Asc Tnr",
"STROM,MEGAN MARIE - CASSH GCL Asc Tnr",
"TOLLEFSON,MARY JANEAN - CASSH Mus Asc Tnr Chr",
"TORIBIO,SHERWIN G - CSH Mth Asc Tnr",
"XU,HONGYING - CASSH GCL Asc Tnr",
"YAN,HUIYA - CSH Mth Prf Tnr",
"ZHANG,LEI - CASSH Eng Asc Tnr"))

IEC <- IEC %>% separate(full, c("name", "deptrank", "note"), " - ")
IEC <- IEC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

IEC.res.ind <- which(originalData$LastName %in% IEC$name)

originalData$IEC[IEC.res.ind] <- "RES"
```

## Library
```{r, message=FALSE, warning=FALSE}
Library <- data.frame(full = c(
"ASCENCIO,CHRISTINE ALICE - CBA Mgt Ast",
"BUTLER MODAFF,JENNIFER - CASSH CST Asc Tnr",
"CHEN,WEN-CHIANG R - SOEe Eds Asc Tnr",
"CLUPPERT,INGA JOHANNA - CSH Hpf AstCl",
"DAMALI,UZAY - CBA Mgt Ast",
"DAS,TUSHAR - CSH Mth Asc Tnr",
"ERAMUDUGODA GAMAGE,RANDIKA SANJEEWA - CBA Mgt Ast",
"GARCIA,MERIDETH MARIE - CASSHe Eng Ast",
"GREINER,THOMAS - CSH Hpf Asc Tnr",
"HAN,YE - CBA IS Ast",
"HARDY,PENELOPE KATE - CASSH His Ast",
"HEASER,SARA A - CASSH Eng AscTe",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"IWAI,SHUMA - CASSH RGS AscTe",
"KING,SETH T - CSH Phy Asc Tnr",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"KRAGE,VALERIE ANNE - SOE Eds AscTe",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"LAN,HAIXIA W - CASSH Eng Prf Tnr",
"MASTERS,HEIDI LYNN - SOEe Eds Asc",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NARCOTTA-WELP,EILEEN M - CSH ESS Asc Tnr",
"PARMETER,GREGORY GEORGE - CASSH ThA Ast",
"ROSS JR,WILLIAM H - CBA Mgt Prf Tnr",
"SAUPPE,JASON J - CSH CS Ast Tnr",
"SCHAAF,LUKE J - CASSH Eng AscTe",
"STOBB,WILLIAM E - CASSH Eng Prf Tnr",
"STRAUSS,ERIC A - CSH Bio Prf Tnr",
"ZHANG,LEI - CASSH Eng Asc Tnr"))

Library <- Library %>% separate(full, c("name", "deptrank", "note"), " - ")
Library <- Library %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

Library.res.ind <- which(originalData$LastName %in% Library$name)

originalData$Library[Library.res.ind] <- "RES"
```

## Promotion, Tenure, and Salary
```{r, message=FALSE, warning=FALSE}
PTS <- data.frame(full = c(
"BIGEL,ALAN I - CASSH Pol Prf Tnr",
"BORAH,NILAKSHI - CBA Fin Asc Tnr",
"BOSER,BETH L - CASSH CST Asc Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"DAS,TUSHAR - CSH Mth Asc Tnr",
"GHEIDI,NAGHMEH - CSH ESS Ast Tnr",
"HER,VINCENT K - CASSH Ant Asc Tnr",
"HYSON,DANIEL M - CASSHe Psy Asc Tnr",
"KIERSCH,CHRISTA E - CBA Mgt Asc Tnr",
"LONGHURST,JAMES L - CASSH His Prf Tnr",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NANDIALATH,ANUP MENON - CBA Mgt Asc Tnr",
"NARCOTTA-WELP,EILEEN M - CSH ESS Asc Tnr",
"PERIYASAMY,KASILINGAM - CSH CS Prf Tnr",
"ZHANG,LEI - CASSH Eng Asc Tnr"))

PTS <- PTS %>% separate(full, c("name", "deptrank", "note"), " - ")
PTS <- PTS %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

PTS.res.ind <- which(originalData$LastName %in% PTS$name)

originalData$PTS[PTS.res.ind] <- "RES"
```

## Research and Grants
```{r, message=FALSE, warning=FALSE}
RGC <- data.frame(full = c(
"BABAKHANI TEIMOURI,SHEIDA - CBA Ecn Asc Tnr",
"BEYER,KEITH D - CSH Chm Prf Tnr",
"BORJA RABAGO,JONATHAN - CASSH Mus Asc Tnr",
"BREAUX,RICHARD M - CASSH RGS Asc Tnr",
"BUTLER MODAFF,JENNIFER - CASSH CST Asc Tnr",
"CALDWELL,JACOB TROY - CSH ESS Ast",
"CEDERGREN,ANDERS R - CSH HEd Ast Tnr",
"CHEN,SONG - CSH Mth Asc Tnr",
"CURRENT,MICHAEL D - CASSH Lib Ast Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"DAVELOS,ANITA LYNNE - CSH Bio Asc Tnr",
"DEASON,GRACE M - CASSH Psy Asc Tnr",
"DRISCOLL,ADAM ROURKE - CASSH Soc Ast Tnr",
"GHEIDI,NAGHMEH - CSH ESS Ast Tnr",
"GILMORE,GARY D - CSH HEd Prf Tnr",
"GREINER,THOMAS - CSH Hpf Asc Tnr",
"HEASER,SARA A - CASSH Eng AscTe",
"KIL,NAM YUN - CSH Rec Ast",
"KING,SETH T - CSH Phy Asc Tnr",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"LIU,SHIANG - CBA Fin Ast",
"MITRA,DIPANKAR - CSH CS Ast",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NANDIALATH,ANUP MENON - CBA Mgt Asc Tnr",
"OSMUNDSON,TODD W - CSH Bio Prf Tnr",
"SAMBU,DANIEL K - CSH Geo Asc Tnr",
"SCHNEIDER,DANIEL C - CASSH Phl Ast",
"SCHUMANN,DAVID J - CSH Bio Ast",
"STARCK,JENNA R - CSHe ESS Ast",
"THAKKAR,TANVI D - CASSH Psy Lec",
"VAUGHN,CODY NATHANIEL - CBA Ecn Ast",
"WILKER,PETER R - CSH Mic Asc Tnr",
"XU,HONGYING - CASSH GCL Asc Tnr",
"ZABEL,KEVIN LEE - CASSH Psy Ast",
"ZHANG,LEI - CASSH Eng Asc Tnr"))

RGC <- RGC %>% separate(full, c("name", "deptrank", "note"), " - ")
RGC <- RGC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

RGC.res.ind <- which(originalData$LastName %in% RGC$name)

originalData$RGC[RGC.res.ind] <- "RES"
```

## Scholarships and Awards
```{r, message=FALSE, warning=FALSE}
SAC <- data.frame(full = c(
"ANNINO,DAVID - CBA IS AscTe",
"BEYER,KEITH D - CSH Chm Prf Tnr",
"BIGEL,ALAN I - CASSH Pol Prf Tnr",
"BINGHAM,MELISSA A - CSH Mth Prf Tnr",
"BOSER,BETH L - CASSH CST Asc Tnr",
"BREAUX,RICHARD M - CASSH RGS Asc Tnr",
"BUTLER MODAFF,JENNIFER - CASSH CST Asc Tnr",
"CHEN,SONG - CSH Mth Asc Tnr",
"CHERGOSKY,ANTHONY JACOB - CASSH Pol Ast",
"CLUPPERT,INGA JOHANNA - CSH Hpf AstCl",
"CURRENT,MICHAEL D - CASSH Lib Ast Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"DEFAZIO,KIMBERLY - CASSH Eng Asc Tnr",
"DRISCOLL,ADAM ROURKE - CASSH Soc Ast Tnr",
"GHEIDI,NAGHMEH - CSH ESS Ast Tnr",
"HARDY,PENELOPE KATE - CASSH His Ast",
"HART,KAREN STUART - CASSH Eng PrfTe",
"HEASER,SARA A - CASSH Eng AscTe",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"KRAGE,VALERIE ANNE - SOE Eds AscTe",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"LAVELLE,KATHERINE L - CASSH CST Asc Tnr",
"LAZZARI,MICHAEL A - CSH Mic AscCl",
"LEACH,MEGAN - CBA Acc Ast",
"LEVINSON,LINDA C - CASSH Art Prf Tnr",
"MITRA,DIPANKAR - CSH CS Ast",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NELSON,KENDRIC J - CSH Chm Ast Tnr",
"NEUKOM,JOSHUA D - CSH Chm AscTe",
"OLSON,MICHELLE R - CSH Hpf AstCl",
"PITOT,LISA NOEL - SOEe Eds Ast",
"ROSS JR,WILLIAM H - CBA Mgt Prf Tnr",
"SCHWARTZ,CHRISTINE P - CSH Bio Asc Tnr",
"SEN,SUJAT - CSH Chm Ast",
"THAKKAR,TANVI D - CASSH Psy Lec",
"TOLLEFSON,MARY JANEAN - CASSH Mus Asc Tnr Chr",
"TORIBIO,SHERWIN G - CSH Mth Asc Tnr",
"TUROV,YEVGENIYA - CSH Chm AscTe",
"VAUGHN,CODY NATHANIEL - CBA Ecn Ast",
"VEERASAMY,SUTHAKARAN - CASSH Psy Ast Tnr",
"WAGNER,SHELDON ERIC - CSH ESS AscTe",
"WARNBERG,NATHAN JOEL - CSH Mth Asc Tnr",
"WHITNEY,EMILY A - CSH HEd Asc Tnr",
"WISINSKI,JACLYN ANNE - CSH Bio Ast",
"XU,HONGYING - CASSH GCL Asc Tnr",
"ZABEL,KEVIN LEE - CASSH Psy Ast"))

SAC <- SAC %>% separate(full, c("name", "deptrank", "note"), " - ")
SAC <- SAC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

SAC.res.ind <- which(originalData$LastName %in% SAC$name)

originalData$SAC[SAC.res.ind] <- "RES"
```

## Undergraduate Academic Program Review
```{r, message=FALSE, warning=FALSE}
UAPR <- data.frame(full = c(
"HARDY,PENELOPE KATE - CASSH His Ast",
"KOPP,BRYAN M - CASSH Eng Asc Tnr",
"MITRA,DIPANKAR - CSH CS Ast",
"PARMETER,GREGORY GEORGE - CASSH ThA Ast",
"THAKKAR,TANVI D - CASSH Psy Lec",
"WHITNEY,EMILY A - CSH HEd Asc Tnr"))

UAPR <- UAPR %>% separate(full, c("name", "deptrank", "note"), " - ")
UAPR <- UAPR %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

UAPR.res.ind <- which(originalData$LastName %in% UAPR$name)

originalData$UAPR[UAPR.res.ind] <- "RES"
```

## Undergraduate Curriculum
```{r, message=FALSE, warning=FALSE}
UCC <- data.frame(full = c(
"BOSER,BETH L - CASSH CST Asc Tnr",
"CEDERGREN,ANDERS R - CSH HEd Ast Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"EPSTEIN,ANN M - SOEe Eds Prf Tnr",
"ESKEW,STEWART SCOTT - CASSH Phl Lec",
"FLEMING,ANNA MARIE - SOE FExp Lec",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"KIM,EDWARD D - CSH Mth Asc Tnr",
"KIRSCH,JANET E - CSH Chm Asc Tnr",
"LEACH,MEGAN - CBA Acc Ast",
"PETERSON,JESSICA MARIE - CASSH CST AstTe",
"SAUPPE,JASON J - CSH CS Ast Tnr",
"SCHAAF,LUKE J - CASSH Eng AscTe",
"THAKKAR,TANVI D - CASSH Psy Lec",
"TORIBIO,SHERWIN G - CSH Mth Asc Tnr",
"XU,HONGYING - CASSH GCL Asc Tnr"))

UCC <- UCC %>% separate(full, c("name", "deptrank", "note"), " - ")
UCC <- UCC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

UCC.res.ind <- which(originalData$LastName %in% UCC$name)

originalData$UCC[UCC.res.ind] <- "RES"
```

## Undergraduare Research
```{r, message=FALSE, warning=FALSE}
URC <- data.frame(full = c(
"ANDERSON,ROBERT BRANDON - CASSH CST Ast",
"BOSER,BETH L - CASSH CST Asc Tnr",
"BRUNDAGE,CORD MICHAEL - CSH Bio Lec",
"BUTLER MODAFF,JENNIFER - CASSH CST Asc Tnr",
"CALDWELL,JACOB TROY - CSH ESS Ast",
"CEDERGREN,ANDERS R - CSH HEd Ast Tnr",
"CHEN,SONG - CSH Mth Asc Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"DAVELOS,ANITA LYNNE - CSH Bio Asc Tnr",
"DOBBS,WARD C - CSH ESS Ast",
"DRISCOLL,ADAM ROURKE - CASSH Soc Ast Tnr",
"ESKEW,STEWART SCOTT - CASSH Phl Lec",
"GALBRAITH,ANNE M - CSH Bio Asc Tnr",
"GHEIDI,NAGHMEH - CSH ESS Ast Tnr",
"GIBLIN,NAOKO AMINAKA - CSH ESS Asc Tnr",
"GOODNOW,REGINA R - CASSH Pol Asc Tnr Chr",
"HARDY,PENELOPE KATE - CASSH His Ast",
"HART,KAREN STUART - CASSH Eng PrfTe",
"HEASER,SARA A - CASSH Eng AscTe",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"KING,SETH T - CSH Phy Asc Tnr",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"LU,WEIXU - CASSH CST Ast",
"MITRA,DIPANKAR - CSH CS Ast",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NANDIALATH,ANUP MENON - CBA Mgt Asc Tnr",
"NASIF,NESE - CBA Mkt Ast",
"OSMUNDSON,TODD W - CSH Bio Prf Tnr",
"PARMETER,GREGORY GEORGE - CASSH ThA Ast",
"PEACOCK,ELIZABETH A - CASSH Ant Asc Tnr",
"PITOT,LISA NOEL - SOEe Eds Ast",
"PLUNKETT,DANIEL K - CSH Rec Asc Tnr",
"SANDERFOOT,ANTON A - CSH Bio Asc Tnr",
"SCHAAF,LUKE J - CASSH Eng AscTe",
"SCHUMANN,DAVID J - CSH Bio Ast",
"SEN,SUJAT - CSH Chm Ast",
"STOVEY,PATRICIA ANN - CASSH His Ast Tnr",
"STRAUSS,ERIC A - CSH Bio Prf Tnr",
"STROM,MEGAN MARIE - CASSH GCL Asc Tnr",
"THAKKAR,TANVI D - CASSH Psy Lec",
"WARNBERG,NATHAN JOEL - CSH Mth Asc Tnr",
"WILKER,PETER R - CSH Mic Asc Tnr",
"WISINSKI,JACLYN ANNE - CSH Bio Ast",
"ZABEL,KEVIN LEE - CASSH Psy Ast",
"ZHANG,LEI - CASSH Eng Asc Tnr"))

URC <- URC %>% separate(full, c("name", "deptrank", "note"), " - ")
URC <- URC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

URC.res.ind <- which(originalData$LastName %in% URC$name)

originalData$URC[URC.res.ind] <- "RES"
```

## University Program Assessment Committee
```{r, message=FALSE, warning=FALSE}
UPAC <- data.frame(full = c(
"BABAKHANI TEIMOURI,SHEIDA - CBA Ecn Asc Tnr",
"BUTLER MODAFF,JENNIFER - CASSH CST Asc Tnr",
"CLUPPERT,INGA JOHANNA - CSH Hpf AstCl",
"DAMALI,UZAY - CBA Mgt Ast",
"MITRA,DIPANKAR - CSH CS Ast",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NEWTON,JOCELYN H - CASSHe Psy Prf Tnr Chr",
"THAKKAR,TANVI D - CASSH Psy Lec"))

UPAC <- UPAC %>% separate(full, c("name", "deptrank", "note"), " - ")
UPAC <- UPAC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

UPAC.res.ind <- which(originalData$LastName %in% UPAC$name)

originalData$UPAC[UPAC.res.ind] <- "RES"
```

## Joint - Environmental Sustainability
```{r, message=FALSE, warning=FALSE}
JES <- data.frame(full = c(
"ASCENCIO,CHRISTINE ALICE - CBA Mgt Ast",
"GOLDEN,BENJAMIN JAMES - CASSH ThA AscTe",
"GOODNOW,REGINA R - CASSH Pol Asc Tnr Chr",
"HARDY,PENELOPE KATE - CASSH His Ast",
"KORTENKAMP,KATHERINE V - CASSH Psy Asc Tnr",
"KRAGE,VALERIE ANNE - SOE Eds AscTe",
"NEUKOM,JOSHUA D - CSH Chm AscTe",
"PETTIT,MICHELE L - CSH HEd Asc Tnr",
"SCHNEIDER,DANIEL C - CASSH Phl Ast",
"SCHWARTZ,CHRISTINE P - CSH Bio Asc Tnr",
"WHITNEY,EMILY A - CSH HEd Asc Tnr"))

JES <- JES %>% separate(full, c("name", "deptrank", "note"), " - ")
JES <- JES %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

JES.res.ind <- which(originalData$LastName %in% JES$name)

originalData$JEnvSus[JES.res.ind] <- "RES"
```

## Joint Committee on Free Speech Promotion
```{r, message=FALSE, warning=FALSE}
JCFSP <- data.frame(full = c(
"ANDERSON,ROBERT BRANDON - CASSH CST Ast",
"BABAKHANI TEIMOURI,SHEIDA - CBA Ecn Asc Tnr",
"CHERGOSKY,ANTHONY JACOB - CASSH Pol Ast",
"DUTTA,NABAMITA - CBA Ecn Prf Tnr",
"GREINER,THOMAS - CSH Hpf Asc Tnr",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NARCOTTA-WELP,EILEEN M - CSH ESS Asc Tnr",
"PARMETER,GREGORY GEORGE - CASSH ThA Ast",
"PETTIT,MICHELE L - CSH HEd Asc Tnr",
"ROBERTS,CHARLOTTE E - SOEe Eds Ast",
"WYMAN,CHELSEA T - CASSH Lib Ast",
"ZAMPARUTTI,LOUISE E - CASSH Eng Ast"))

JCFSP <- JCFSP %>% separate(full, c("name", "deptrank", "note"), " - ")
JCFSP <- JCFSP %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

JCFSP.res.ind <- which(originalData$LastName %in% JCFSP$name)

originalData$JCFSP[JCFSP.res.ind] <- "RES"
```

## Joint - Multicultural Affairs
```{r, message=FALSE, warning=FALSE}
JMAC <- data.frame(full = c(
"BABAKHANI TEIMOURI,SHEIDA - CBA Ecn Asc Tnr",
"CHEN,SONG - CSH Mth Asc Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"ESKEW,STEWART SCOTT - CASSH Phl Lec",
"GIBLIN,NAOKO AMINAKA - CSH ESS Asc Tnr",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"KABASHI,LEMA - SOEe Eds Asc Tnr",
"KOPP,BRYAN M - CASSH Eng Asc Tnr",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NARCOTTA-WELP,EILEEN M - CSH ESS Asc Tnr",
"PARMETER,GREGORY GEORGE - CASSH ThA Ast",
"PETTIT,MICHELE L - CSH HEd Asc Tnr",
"SANDERFOOT,ANTON A - CSH Bio Asc Tnr",
"THAKKAR,TANVI D - CASSH Psy Lec",
"TUROV,YEVGENIYA - CSH Chm AscTe",
"WYMAN,CHELSEA T - CASSH Lib Ast"))

JMAC <- JMAC %>% separate(full, c("name", "deptrank", "note"), " - ")
JMAC <- JMAC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

JMAC.res.ind <- which(originalData$LastName %in% JMAC$name)

originalData$JMAC[JMAC.res.ind] <- "RES"
```

## Joint - Planning & Budget
```{r, message=FALSE, warning=FALSE}
JPB <- data.frame(full = c(
"DAMALI,UZAY - CBA Mgt Ast",
"NANDIALATH,ANUP MENON - CBA Mgt Asc Tnr",
"ORMES,GREGORY F - CASSH CST Ast Tnr",
"WAGNER,SHELDON ERIC - CSH ESS AscTe",
"WILKER,PETER R - CSH Mic Asc Tnr"))

JPB <- JPB %>% separate(full, c("name", "deptrank", "note"), " - ")
JPB <- JPB %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

JPB.res.ind <- which(originalData$LastName %in% JPB$name)

originalData$JPB[JPB.res.ind] <- "RES"
```

## Joint - Legislative / Regents
```{r, message=FALSE, warning=FALSE}
LegReg <- data.frame(full = c(
"APONTE-SAFE,GERARDO JOEL - SOEe Eds Ast",
"BIGEL,ALAN I - CASSH Pol Prf Tnr",
"CEDERGREN,ANDERS R - CSH HEd Ast Tnr",
"DAVELOS,ANITA LYNNE - CSH Bio Asc Tnr",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"LONGHURST,JAMES L - CASSH His Prf Tnr",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"PETERSON,JESSICA MARIE - CASSH CST AstTe",
"PETULLO,WILLIAM M - CSH CS Ast",
"THAKKAR,TANVI D - CASSH Psy Lec"))

LegReg <- LegReg %>% separate(full, c("name", "deptrank", "note"), " - ")
LegReg <- LegReg %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

LegReg.res.ind <- which(originalData$LastName %in% LegReg$name)

originalData$LegReg[LegReg.res.ind] <- "RES"
```

## Parking Appeals
```{r, message=FALSE, warning=FALSE}
PA <- data.frame(full = c(
"BIGEL,ALAN I - CASSH Pol Prf Tnr",
"CAMPBELL,PATRICIA A - CSH Hpf AscCl",
"CLUPPERT,INGA JOHANNA - CSH Hpf AstCl",
"DAMALI,UZAY - CBA Mgt Ast",
"GREINER,THOMAS - CSH Hpf Asc Tnr",
"HOFFER,ADAM J - CBA Ecn Asc Tnr",
"KING,SETH T - CSH Phy Asc Tnr",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"LEACH,MEGAN - CBA Acc Ast",
"MASTERS,HEIDI LYNN - SOEe Eds Asc",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"PARMETER,GREGORY GEORGE - CASSH ThA Ast",
"REDMAN,RENEE S - CSH Bio PrfTe",
"TAYLOR,JENNIFER DAWN - CSH Rec Ast",
"TUROV,YEVGENIYA - CSH Chm AscTe",
"TUTTLE ROSS,SHERYL - CASSH Phl Prf Tnr",
"WILKER,PETER R - CSH Mic Asc Tnr"))

PA <- PA %>% separate(full, c("name", "deptrank", "note"), " - ")
PA <- PA %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

PA.res.ind <- which(originalData$LastName %in% PA$name)

originalData$PkgAppls[PA.res.ind] <- "RES"
```

## Textbook Services Oversight
```{r, message=FALSE, warning=FALSE}
TSO <- data.frame(full = c(
"BIGEL,ALAN I - CASSH Pol Prf Tnr",
"BOSER,BETH L - CASSH CST Asc Tnr",
"CRUTCHFIELD,SUSAN - CASSH Eng Asc Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"DEASON,GRACE M - CASSH Psy Asc Tnr",
"FOWLER,REBEKAH M - CASSH Eng Asc Tnr",
"HARDY,PENELOPE KATE - CASSH His Ast",
"IGUCHI,GERALD S - CASSH His Asc Tnr",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"LONGHURST,JAMES L - CASSH His Prf Tnr",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"PARMETER,GREGORY GEORGE - CASSH ThA Ast",
"TUROV,YEVGENIYA - CSH Chm AscTe",
"VAUGHN,CODY NATHANIEL - CBA Ecn Ast",
"XU,HONGYING - CASSH GCL Asc Tnr"))

TSO <- TSO %>% separate(full, c("name", "deptrank", "note"), " - ")
TSO <- TSO %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

TSO.res.ind <- which(originalData$LastName %in% TSO$name)

originalData$TxtBook[TSO.res.ind] <- "RES"
```

## Student - Academic Initiatives
```{r, message=FALSE, warning=FALSE}
AIDAC <- data.frame(full = c(
"APONTE-SAFE,GERARDO JOEL - SOEe Eds Ast",
"DAMALI,UZAY - CBA Mgt Ast",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"LEACH,MEGAN - CBA Acc Ast",
"MITRA,DIPANKAR - CSH CS Ast",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"PETERSON,JESSICA MARIE - CASSH CST AstTe"))

AIDAC <- AIDAC %>% separate(full, c("name", "deptrank", "note"), " - ")
AIDAC <- AIDAC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

AIDAC.res.ind <- which(originalData$LastName %in% AIDAC$name)

originalData$AIDAC[AIDAC.res.ind] <- "RES"
```

## Student - Athletics
```{r, message=FALSE, warning=FALSE}
ATH <- data.frame(full = c(
"ANNINO,DAVID - CBA IS AscTe",
"CEDERGREN,ANDERS R - CSH HEd Ast Tnr",
"CHERGOSKY,ANTHONY JACOB - CASSH Pol Ast",
"CLUPPERT,INGA JOHANNA - CSH Hpf AstCl",
"DAMALI,UZAY - CBA Mgt Ast",
"DAVELOS,ANITA LYNNE - CSH Bio Asc Tnr",
"DOBBS,WARD C - CSH ESS Ast",
"HOFFER,ADAM J - CBA Ecn Asc Tnr",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NARCOTTA-WELP,EILEEN M - CSH ESS Asc Tnr",
"REDMAN,RENEE S - CSH Bio PrfTe",
"ROBERTS,CHARLOTTE E - SOEe Eds Ast",
"SCHMIDT,SAMUEL - CSH ESS Ast",
"STOBB,WILLIAM E - CASSH Eng Prf Tnr",
"WISINSKI,JACLYN ANNE - CSH Bio Ast",
"ZABEL,KEVIN LEE - CASSH Psy Ast"))

ATH <- ATH %>% separate(full, c("name", "deptrank", "note"), " - ")
ATH <- ATH %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

ATH.res.ind <- which(originalData$LastName %in% ATH$name)

originalData$Ath[ATH.res.ind] <- "RES"
```

## Student - Campus Community Enrichment Fund Committee
```{r, message=FALSE, warning=FALSE}
CCEFC <- data.frame(full = c(
"BHATTACHARYYA,BASUDEB - CSH Chm AscTe",
"CHEN,SONG - CSH Mth Asc Tnr",
"CHERGOSKY,ANTHONY JACOB - CASSH Pol Ast",
"CRUTCHFIELD,SUSAN - CASSH Eng Asc Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"LAUFENBERG,MAGGIE R - CSH Hpf AstCl",
"LEACH,MEGAN - CBA Acc Ast",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"ZABEL,KEVIN LEE - CASSH Psy Ast"))

CCEFC <- CCEFC %>% separate(full, c("name", "deptrank", "note"), " - ")
CCEFC <- CCEFC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

CCEFC.res.ind <- which(originalData$LastName %in% CCEFC$name)

originalData$CCEFC[CCEFC.res.ind] <- "RES"
```

## Student - Legislative Affairs
```{r, message=FALSE, warning=FALSE}
SLA <- data.frame(full = c(
"BUTLER MODAFF,JENNIFER - CASSH CST Asc Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"DAVELOS,ANITA LYNNE - CSH Bio Asc Tnr",
"MORRISON,HEIDI - CASSH His Asc Tnr"))

SLA <- SLA %>% separate(full, c("name", "deptrank", "note"), " - ")
SLA <- SLA %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

SLA.res.ind <- which(originalData$LastName %in% SLA$name)

originalData$LegAffrs[SLA.res.ind] <- "RES"
```

## Student - Organizations
```{r, message=FALSE, warning=FALSE}
SOrg <- data.frame(full = c(
"BABAKHANI TEIMOURI,SHEIDA - CBA Ecn Asc Tnr",
"BUTLER MODAFF,JENNIFER - CASSH CST Asc Tnr",
"CHERGOSKY,ANTHONY JACOB - CASSH Pol Ast",
"CLUPPERT,INGA JOHANNA - CSH Hpf AstCl",
"CRUTCHFIELD,SUSAN - CASSH Eng Asc Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"KABASHI,LEMA - SOEe Eds Asc Tnr",
"KUMM-SCHALEY,BRIAN EDWARD - CSH Rec Asc Tnr",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"PFITZINGER,SCOTT G - CASSH Lib Ast Tnr",
"REDMAN,RENEE S - CSH Bio PrfTe",
"THAKKAR,TANVI D - CASSH Psy Lec",
"TUROV,YEVGENIYA - CSH Chm AscTe",
"WHITNEY,EMILY A - CSH HEd Asc Tnr",
"WISINSKI,JACLYN ANNE - CSH Bio Ast",
"ZIMMERMAN,MARY ANN - CSH Bio Ast"))

SOrg <- SOrg %>% separate(full, c("name", "deptrank", "note"), " - ")
SOrg <- SOrg %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

SOrg.res.ind <- which(originalData$LastName %in% SOrg$name)

originalData$Org[SOrg.res.ind] <- "RES"
```

## Student - Services & Buildings
```{r, message=FALSE, warning=FALSE}
SSB <- data.frame(full = c(
"BUTLER MODAFF,JENNIFER - CASSH CST Asc Tnr",
"DAMALI,UZAY - CBA Mgt Ast",
"IWAI,SHUMA - CASSH RGS AscTe",
"MITRA,DIPANKAR - CSH CS Ast",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"PFITZINGER,SCOTT G - CASSH Lib Ast Tnr",
"WHITNEY,EMILY A - CSH HEd Asc Tnr"))

SSB <- SSB %>% separate(full, c("name", "deptrank", "note"), " - ")
SSB <- SSB %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

SSB.res.ind <- which(originalData$LastName %in% SSB$name)

originalData$ServBldg[SSB.res.ind] <- "RES"
```

## Student - Segregated University Fee Allocation
```{r, message=FALSE, warning=FALSE}
SUFAC <- data.frame(full = c(
"DAMALI,UZAY - CBA Mgt Ast",
"FISHER,TAMMY M - CASSHe Mus Asc Tnr",
"LEACH,MEGAN - CBA Acc Ast",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"NARCOTTA-WELP,EILEEN M - CSH ESS Asc Tnr",
"PETERSON,JESSICA MARIE - CASSH CST AstTe"))

SUFAC <- SUFAC %>% separate(full, c("name", "deptrank", "note"), " - ")
SUFAC <- SUFAC %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

SUFAC.res.ind <- which(originalData$LastName %in% SUFAC$name)

originalData$SUFAC[SUFAC.res.ind] <- "RES"
```

## Student - Green Fund
```{r, message=FALSE, warning=FALSE}
GREEFND <- data.frame(full = c(
"DAMALI,UZAY - CBA Mgt Ast",
"GOODNOW,REGINA R - CASSH Pol Asc Tnr Chr",
"HARDY,PENELOPE KATE - CASSH His Ast",
"KOLBE,AMANDA JOY - CASSH ThA Ast Tnr",
"KOPP,BRYAN M - CASSH Eng Asc Tnr",
"KRAGE,VALERIE ANNE - SOE Eds AscTe",
"MORRISON,HEIDI - CASSH His Asc Tnr",
"SAMBU,DANIEL K - CSH Geo Asc Tnr",
"SCHAAF,LUKE J - CASSH Eng AscTe"))

GREEFND <- GREEFND %>% separate(full, c("name", "deptrank", "note"), " - ")
GREEFND <- GREEFND %>% separate(deptrank, c("college", "dept", "rank", "tnr"), " ")

GREEFND.res.ind <- which(originalData$LastName %in% GREEFND$name)

originalData$GREEFND[GREEFND.res.ind] <- "RES"
```
